Modal Abstractions for Virtualizing Memory Addresses

### 2024-06-29 examples.tex
+

;;pte_t *walkpgdir_succ(pte_t *pml4, const void *va) 
push   rbp
mov    rsp,rbp
sub    0x40,rsp
mov    rdi,-0x8[rbp]
mov    rsi,-0x10[rbp]
;;pte_t *pml4_entry = &pml4[PML4EX(va)];
mov    -0x8[rbp],[rsi]
mov    -0x10[rbp],rdi
shr    0x27,rdi
and    0x1ff,rdi
shl    0x3,rdi
add    rdi,rsi
mov    rsi,-0x18[rbp]
;;pte_t *pdp = pte_get_next_table_succ(pml4_entry);
mov    -0x18[rbp],rdi
callq  <pte_get_next_table_succ>
mov    rax,-0x20[rbp]
;;pte_t *pdp_entry = &pdp[PDPEX(va)];
mov    -0x20[rbp],rax
mov    -0x10[rbp],rsi
shr    0x1e,rsi
and    0x1ff,rsi
shl    0x3,rsi
add    rsi,rax
mov    rax,-0x28[rbp]
;;pte_t *pd = pte_get_next_table_succ(pdp_entry);
mov    -0x28[rbp],rdi
callq  <pte_get_next_table_succ>
mov    rax,-0x30[rbp]
;;pte_t *pd_entry = &pd[PDEX(va)];
mov    -0x30[rbp],rax
mov    -0x10[rbp],rsi
shr    0x15,rsi
and    0x1ff,rsi
shl    0x3,rsi
add    rsi,rax
mov    rax,-0x38[rbp]
;;pte_t *pt = pte_get_next_table_succ(pd_entry);
mov    -0x38[rbp],rdi
callq  <pte_get_next_table_succ>
mov    rax,-0x40[rbp]
;;return &pt[PTEX(va)];
mov    -0x40[rbp],rax
mov    -0x10[rbp],rsi
shr    0xc,rsi
and    0x1ff,rsi
shl    0x3,rsi
add    rsi,rax
add    0x40,rsp
pop    rbp
retq   
  \end{lstlisting}&
  \begin{lstlisting}[mathescape,basicstyle=\scriptsize\ttfamily]
   $\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m) \ast \ulcorner \textsf{OFF} + \paddr > 0 \urcorner \ast \texttt{rbx}\mapsto_{\textsf{r}} \paddr \ast \sumapaces\rtv\delta  \ast \sumpv\paddr\qfrac\true  }_{\rtv}$
;; pte_t *pte_get_next_table_succ(pte_t *entry) {
push   rbp
mov    rsp,rbp
sub    0x20,rsp
mov    rdi,-0x8[rbp]
;;  pte_t *next;
mov    -0x8[rbp],rdi
mov    [rdi],rdi
and    0x1,rdi
mov    rdi,rax
;;  if (!entry->present) {
cmp    0x0,rax
jne    161 <pte_get_next_table_succ+0xa1>
lea    -0x10[rbp],rdi
;;pte_initialize(&next);
callq  70 <pte_initialize>
mov    -0x8[rbp],rdi
mov    [rdi],rax
;;setting the fields of the entry with a fresh allocated page
;;entry->writable = 1
;;entry->user_acc = 1;
;;entry->pfn = PTE_ADDR_TO_PHYS_PFN((uintptr_t) next);
;;entry->present = 1;
and    0xfffffffffffffffd,rax
or     0x2,rax
mov    rax,[rdi]
...
;;}
;;uintptr_t next_virt_addr = (uintptr_t) P2V(next_phys_addr);
mov    -0x8[rbp],rax
mov    [rax],rax
shr    0xc,rax
movabs 0xffffffffff,rcx
and    rcx,rax
shl    0xc,rax
mov    rax,-0x18[rbp]
;;uintptr_t next_virt_addr = (uintptr_t) P2V(next_phys_addr);
mov    -0x18[rbp],rax
movabs 0x0,rcx	187: R_X86_64_64	KERN_BASE
add    rcx,rax
;;next = (pte_t *) next_virt_addr;
mov    rax,-0x20[rbp]
mov    -0x20[rbp],rax
mov    rax,-0x10[rbp]
;;return next
mov    -0x10[rbp],rax
add    0x20,rsp
pop    rbp
ret
  \end{lstlisting}
  \end{tabular}
\vspace{-1em}
\caption{ in Figure \ref{fig:walkpgdir}.}
\label{fig:getnexttable}
\end{figure*}

>>>>

;;pte_t *walkpgdir_succ(pte_t *pml4, const void *va) 
push   rbp
mov    rsp,rbp
sub    0x40,rsp
mov    rdi,-0x8[rbp]
mov    rsi,-0x10[rbp]
;;pte_t *pml4_entry = &pml4[PML4EX(va)];
mov    -0x8[rbp],[rsi]
mov    -0x10[rbp],rdi
shr    0x27,rdi
and    0x1ff,rdi
shl    0x3,rdi
add    rdi,rsi
mov    rsi,-0x18[rbp]
;;pte_t *pdp = pte_get_next_table_succ(pml4_entry);
mov    -0x18[rbp],rdi
callq  <pte_get_next_table_succ>
mov    rax,-0x20[rbp]
;;pte_t *pdp_entry = &pdp[PDPEX(va)];
...
...
...
;;last call at L1 for virtual address to physical page 
callq  <pte_get_next_table_succ>
mov    rax,-0x40[rbp]
;;return &pt[PTEX(va)];
mov    -0x40[rbp],rax
mov    -0x10[rbp],rsi
shr    0xc,rsi
and    0x1ff,rsi
shl    0x3,rsi
add    rsi,rax
add    0x40,rsp
pop    rbp
retq   
  \end{lstlisting}&
  \begin{lstlisting}[mathescape,basicstyle=\scriptsize\ttfamily]
   $\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m) \ast \ulcorner \textsf{OFF} + \paddr > 0 \urcorner \ast \texttt{rbx}\mapsto_{\textsf{r}} \paddr \ast \sumapaces\rtv\delta  \ast \sumpv\paddr\qfrac\true  }_{\rtv}$
;; pte_t *pte_get_next_table_succ(pte_t *entry) {
push   rbp
mov    rsp,rbp
sub    0x20,rsp
mov    rdi,-0x8[rbp]
;;  pte_t *next;
mov    -0x8[rbp],rdi
mov    [rdi],rdi
and    0x1,rdi
mov    rdi,rax
;;  if (!entry->present) {
cmp    0x0,rax
jne    161 <pte_get_next_table_succ+0xa1>
lea    -0x10[rbp],rdi
;;pte_initialize(&next);
callq  70 <pte_initialize>
mov    -0x8[rbp],rdi
mov    [rdi],rax
;;setting the fields of the entry with a fresh allocated page
;;entry->writable = 1
;;entry->user_acc = 1;
;;entry->pfn = PTE_ADDR_TO_PHYS_PFN((uintptr_t) next);
;;entry->present = 1;
and    0xfffffffffffffffd,rax
or     0x2,rax
mov    rax,[rdi]
...
;;}
;;uintptr_t next_virt_addr = (uintptr_t) P2V(next_phys_addr);
mov    -0x8[rbp],rax
mov    [rax],rax
shr    0xc,rax
movabs 0xffffffffff,rcx
and    rcx,rax
shl    0xc,rax
mov    rax,-0x18[rbp]
;;uintptr_t next_virt_addr = (uintptr_t) P2V(next_phys_addr);
mov    -0x18[rbp],rax
movabs 0x0,rcx	187: R_X86_64_64	KERN_BASE
add    rcx,rax
;;next = (pte_t *) next_virt_addr;
mov    rax,-0x20[rbp]
mov    -0x20[rbp],rax
mov    rax,-0x10[rbp]
;;return next
mov    -0x10[rbp],rax
add    0x20,rsp
pop    rbp
ret
  \end{lstlisting}
  \end{tabular}
\vspace{-1em}
\caption{ in Figure \ref{fig:walkpgdir}.}
\label{fig:getnexttable}
\end{figure*}
